Online {\IterComp}

### 2017-11-17 motivation.tex
minor formats

\begin{table}[h]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{Metric} & \multicolumn{1}{c|}{Speedup/Slowdown} & \multicolumn{1}{c|}{IPC} \\ \hline
Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
1/Runtime                    & 3\% slowdown                                  & \multicolumn{1}{c|}{-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\end{table}

>>>>

\begin{table}[t]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Metric} & \textbf{Speedup/Slowdown} & \textbf{IPC} \\ \hline
\rowcolor{Gray} Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
\rowcolor{Gray}1/Runtime                    & 3\% slowdown                                  & {-}   \\ \hline
\end{tabular}
\caption{Comparison of iterative compilation guided by different metrics.
The oracle is guided by the average speedup over \texttt{-O3} on all inputs.
For IPC and runtime, each optimization was evaluated on a different input.
}
\end{table}
